On Supporting Molecular Visualization on Grid Resources using Visual Programming Environments

### 2008-04-24 opal/documents/grid2008/paper.tex
added more details to Opal section

% TODO: Expand (04/23)
\begin{enumerate}
\item{Scheduling and Cluster Management}
\item{Data management and Persistence}
\item{Security}
\item{Standardized WSDL API}
\item{Argument Description and Dynamic Interface Generation}
\end{enumerate}

- Opal wrapper and GUI: Sriram

- Opal and Opal-CSF4: Sriram

- Data services: Sriram

- Status, more information

@@

>>>>

\begin{enumerate}
\item{{\bf Scheduling and Cluster Management:} Since different sites use
    different schedulers such as SGE \cite{sge}, Condor \cite{condor},
    etc., Opal provides a uniform way to access them via standard APIs such
    as Globus GRAM \cite{gram} and DRMAA \cite{drmaa}. The schedulers are
    simply specified using a properties file, and Opal configures itself
    appropriately to access the schedulers via the appropriate parameters.
    In addition, we are currently also able to submit jobs to the CSF4
    metascheduler \cite{csf4} using its WSRF API \cite{wsrf} as described
    in \cite{opal-gui}.}

\item{{\bf Data management and Persistence:} The Opal toolkit manages the
    job data for a particular run on behalf of the user. Every job is run
    in a separate workspace so that multiple jobs from different users can
    be run concurrently. Furthermore, information about job status and
    outputs is persisted in a database to provide fault-tolerance for the
    services.}

\item{{\bf Security:} Opal services can be configured to use
    transport-level GSI-based \cite{gsi} security so as to restrict access
    to only authorized users.}

\item{{\bf Standardized WSDL API:} All Opal use a standard WSDL so that
    they can accessed in a uniform manner by different clients. We choose
    not to generate application specific WSDLs to avoid regneration of
    client-side stubs and rewriting of clients for every application.}

\item{{\bf Argument Description and Dynamic Interface Generation:} Opal
    services can be optionally configured with an XML specification for the
    command-line arguments. This specification consists of a description
    for flags, tagged and untagged parameters, and grouping of arguments.
    Flags are not ordered and are usually represented with a character
    prefixed with a dash and they activate a functionality in the
    application (e.g. -verbose). Tagged Parameters are usually formed by a
    prefix and input value (e.g. -input <filename>) - they can appear in
    any order. Untagged parameters are not prefixed, and hence their order
    is relevant. The argument description is mainly useful for two purposes
    - for validation of command-line arguments passed to the application,
    and for automatic interface generation. A detailed description of the
    argument description, and automatic generation of Web forms from the
    description is provided in \cite{opal-gui}. A complete lifecycle of
    this process is shown in Figure \ref{fig:opal-gui}.}

\end{enumerate}

@@

The Opal toolkit is freely available from SourceForge, and uses an Open
Source BSD-style license. The current stable version of Opal at the time of
writing this manuscript is 1.9.3, and more information is available from
out website \cite{opal-website}.
